### 2009-11-19 doc/tech_doc/a-rex/arex_tech_doc.tex
correct location of cache tools
add passivetransfer option

The following tools (installed in \emph{\$ARC\_LOCATION/libexec})
exist to help with administration of the cache:

@@

\begin{itemize}
\item \textbf{\textit{joblog}}\textit{={[}path]} -- specifies where to store
log file containing information about started and finished jobs.
\item \textbf{\textit{jobreport}}\textit{={[}URL ... number]} -- specifies
that A-REX has to report information about jobs being processed (started,
finished) to centralized service running at given \textit{URL}. Multiple
entries and multiple URLs are allowed. \textit{number} specifies how
long old records have to be kept if failed to be reported. That value
is specified in days. Last specified value becomes effective.
\item \textbf{\textit{jobreport\_credentials}}\textit{={[}key\_file
    {[}cert\_file {[}ca\_dir]]]} -- specifies the credentials for
  accessing the accounting service.
\item \textbf{\textit{jobreport\_options}}\textit{={[}options]}
  -- specifies additional options for Usage Reporter and/or
  accounting service. The \textit{options} string is interpreted by Usage
  Reporter, its format is described in the corresponding technical document.
\item \textbf{\textit{securetransfer}}\textit{=yes|no} -- specifies whether
to use encryption while transferring data. Currently works for GridFTP
only. Default is \emph{no}. It is overridden by value specified in
URL options.

>>>>

The following tools (installed in \emph{\$ARC\_LOCATION/libexec/arc})
exist to help with administration of the cache:

@@

\begin{itemize}
\item \textbf{\textit{joblog}}\textit{={[}path]} -- specifies where to store
log file containing information about started and finished jobs.
\item \textbf{\textit{jobreport}}\textit{={[}URL ... number]} -- specifies
that A-REX has to report information about jobs being processed (started,
finished) to centralized service running at given \textit{URL}. Multiple
entries and multiple URLs are allowed. \textit{number} specifies how
long old records have to be kept if failed to be reported. That value
is specified in days. Last specified value becomes effective.
\item \textbf{\textit{jobreport\_credentials}}\textit{={[}key\_file
    {[}cert\_file {[}ca\_dir]]]} -- specifies the credentials for
  accessing the accounting service.
\item \textbf{\textit{jobreport\_options}}\textit{={[}options]}
  -- specifies additional options for Usage Reporter and/or
  accounting service. The \textit{options} string is interpreted by Usage
  Reporter, its format is described in the corresponding technical document.
\item \textbf{\textit{securetransfer}}\textit{=yes|no} -- specifies whether
to use encryption while transferring data. Currently works for GridFTP
only. Default is \emph{no}. It is overridden by value specified in
URL options.
\item \textbf{\textit{passivetransfer}}\textit{=yes|no} -- specifies
  whether GridFTP transfers are passive. Setting this option to yes
  can solve transfer problems caused by firewalls. Default is no.
